---
title: "Challenge 4"
subtitle: "Night of the Living R"
output:
  html_document:
    df_print: paged
---

# Challenge 4
These questions are based on the following SWC lessions

- [Writing Data](http://swcarpentry.github.io/r-novice-gapminder/11-writing-data/)
- [Dataframe Manipulation with dplyr](http://swcarpentry.github.io/r-novice-gapminder/13-dplyr/)
- [Dataframe Manipulation with tidyr](http://swcarpentry.github.io/r-novice-gapminder/14-tidyr/)
- [Producing Reports With knitr](http://swcarpentry.github.io/r-novice-gapminder/15-knitr-markdown/)
- [Writing Good Software](http://swcarpentry.github.io/r-novice-gapminder/16-wrap-up/)

## Load Data

You need to load the gapminder data into a dataframe.  You can do this directly from the Internet or download a local copy first.  The URL for the gapminder data is <https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/gh-pages/_episodes_rmd/data/gapminder_data.csv>

```{r}

```

## Writing Data

1. Write the gapminder data from *Angola* and *Argentina* to a file named `gapminder_angola_argentina.csv`.  The file should be in CSV format.  It should have column labels, but should not have row numbers and character strings should not be quoted.  

> Hint: You can do this with a single command, but you don't have to.

```{r}

```


## Dataframe Manipulation with dplyr

2. Use `dplyr` to write a single command (which can span multiple lines and includes pipes) that produces a dataframe containing the data for all entries in gapminder where the population is less than *100000*.  This new dataframe should only have the population, country, continent, and year. Print the dataframe.

```{r}

```



3. Use tools from `dplyr` to make a dataframe with the global *mean* life expectancy for each year in the gapminder dataset.

```{r}

```

## Dataframe Manipulation with tidyr

4. R has several built in dataset.  One of these is `iris`; you can take a peek at it with `head(iris)`.  Use tidyr to make a "long" version of the the iris dataframe.  The long version should have just 3 columns: Species, Measurement, Value.

```{r}

```

## Producing Reports With knitr
### Inline R code
```{r}

```

5. In the following line of text you should replace *YEAR* and *MAX_POP* with inline code so that you can change the year of interest in a variable defined elsewhere and the sentence will be updated when knitted.  *Hint:* We have placed an empty code chunk immediately above this question; you will propably want to define some variables and do other work there so that your inline code is short.

In YEAR the maximum population for any country was MAX_POP.

### Chunk options

6. Add options to the following chunk so that when this document is knitted, the figure is still shown, but the code chunk itself is not.

```{r gapminder_plot}
library("ggplot2")
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
```

### Formatting Text
7. Rmarkdown allows you to format text in a number of ways, including bold, italics, and verbatim code.  Pick one of the formats from the the "Pandoc’s Markdown" section of the [Rmarkdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf) and apply it to the following sentence, then knit this document to confirm that it worked:

Rmarkdown is awesome!



8. Below here you should make a Sub-sub section titled "Halloween Candy", then make a numbered list of your top 3 Halloween treats



# Session Info
Always print `sessionInfo` for reproducibility!
```{r}

```

